A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-01-09 manuscript/manuscript.qmd
added GH and corrected agreement metrics table label

**Authors**: Janick Weberpals^1^, Kenneth L. Kehl^2^, Donna R. Rivera^3^, Pallavi Mishra-Kalyani^3^, Priyanka Anand^1^, ..., Sebastian Schneeweiss^1^, Shirley V. Wang^1^

@@

tbl_metrics <- data |> 
  mutate(across(where(is.numeric), function(x) format(x, digits = 2, nsmall = 2))) |> 
  mutate(
    RCT = glue("{estimate_RCT} ({lower_RCT} - {upper_RCT})"),
    RWE = glue("{estimate_RWE} ({lower_RWE} - {upper_RWE})"),
    smd = glue("{smd} ({smd_value})")
  ) |> 
  select(trial, RCT, RWE, regulatory, estimate, smd) |> 
  gt() |> 
  tab_spanner(
    label = "HR (95% CI)",
    columns = c(RCT, RWE)
  ) |> 
  cols_label(
    trial = "Trial",
    regulatory = md("Regulatory <br> agreement"),
    estimate = md("Estimate <br> agreement"),
    smd = "SMD"
    ) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
    ) |> 
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_spanners()
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), 
    locations = cells_body(
      columns = regulatory,
      rows = regulatory == "Yes"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), 
    locations = cells_body(
      columns = regulatory,
      rows = regulatory == "No"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), 
    locations = cells_body(
      columns = estimate,
      rows = estimate == "Yes"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), 
    locations = cells_body(
      columns = estimate,
      rows = estimate == "No"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), 
    locations = cells_body(
      columns = smd,
      rows = stringr::str_detect(smd, "Yes")
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), 
    locations = cells_body(
      columns = smd,
      rows = stringr::str_detect(smd, "No")
      )
    ) |> 
  tab_footnote("Abbreviations: CI = Confidence interval, HR = Hazard ratio, RCT = Randomized controlled trial, RWE = Real-world evidence, SMD = standardized mean difference (based on log hazard ratios)")

>>>>

**Authors**: Janick Weberpals^1^, Kenneth L. Kehl^2^, Donna R. Rivera^3^, Pallavi Mishra-Kalyani^3^, Georg Hahn^1^, Priyanka Anand^1^, ..., Sebastian Schneeweiss^1^, Shirley V. Wang^1^

@@

tbl_metrics <- data |> 
  mutate(across(where(is.numeric), function(x) format(x, digits = 2, nsmall = 2))) |> 
  mutate(
    RCT = glue("{estimate_RCT} ({lower_RCT} - {upper_RCT})"),
    RWE = glue("{estimate_RWE} ({lower_RWE} - {upper_RWE})"),
    smd = glue("{smd} ({smd_value})")
  ) |> 
  select(trial, RCT, RWE, regulatory, estimate, smd) |> 
  gt() |> 
  tab_spanner(
    label = "HR (95% CI)",
    columns = c(RCT, RWE)
  ) |> 
  cols_label(
    trial = "Trial",
    regulatory = md("Statistical <br> significance <br> agreement"),
    estimate = md("Estimate <br> agreement"),
    smd = "SMD"
    ) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
    ) |> 
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_spanners()
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), 
    locations = cells_body(
      columns = regulatory,
      rows = regulatory == "Yes"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), 
    locations = cells_body(
      columns = regulatory,
      rows = regulatory == "No"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), 
    locations = cells_body(
      columns = estimate,
      rows = estimate == "Yes"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), 
    locations = cells_body(
      columns = estimate,
      rows = estimate == "No"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), 
    locations = cells_body(
      columns = smd,
      rows = stringr::str_detect(smd, "Yes")
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), 
    locations = cells_body(
      columns = smd,
      rows = stringr::str_detect(smd, "No")
      )
    ) |> 
  tab_footnote("Abbreviations: CI = Confidence interval, HR = Hazard ratio, RCT = Randomized controlled trial, RWE = Real-world evidence, SMD = standardized mean difference (based on log hazard ratios)")
